
---
output: 
  html_document:
    keep_md: true
--- 

```{r}
#install and load package arules
library(arules)
#install and load arulesViz
library(arulesViz)
#install and load tidyverse
library(tidyverse)
#install and load readxml
library(readxl)
#install and load knitr
library(knitr)
#load ggplot2 as it comes in tidyverse
library(ggplot2)
#install and load lubridate
library(lubridate)
#install and load plyr
library(plyr)
library(dplyr)

#Set a working directory
setwd("/DataSets")
#load the data
BreadBasket <- read.csv("BreadBasket_DMS.csv")


BreadBasket <- BreadBasket[complete.cases(BreadBasket), ]

# Removing NONE
BreadBasket <- BreadBasket[!(BreadBasket$Item=="NONE"),]

#Factor Item 
BreadBasket %>% mutate(Item = as.factor(Item)) 

#Transaction into numeric type
TransNum = as.numeric(as.character(BreadBasket$Transaction))

#Combine new columns into dataframe BreadBasket
cbind(BreadBasket,TransNum)


#ddply(dataframe, variables_to_be_used_to_split_data_frame, function_to_be_applied)
TransactionData <- ddply(BreadBasket,c("TransNum"),
                         function(df1)paste(df1$Item,
                                            collapse = ","))
TransactionData
TransactionData$TransNum <- NULL
TransactionData

#create Transaction_csv file
write.csv(TransactionData,"transactions_data.csv", quote = FALSE, row.names = FALSE)

TransData <- read.transactions("transactions_data.csv", format = 'basket', sep=',')

TransData
summary(TransData)

# Create an item frequency plot for the top 20 items
if (!require("RColorBrewer")) {
  # install color package of R
  install.packages("RColorBrewer")
  #include library RColorBrewer
  library(RColorBrewer)
}

#Absolute Item Frequency Plot which list all the distincts items in summary
itemFrequencyPlot(TransData,topN=20,type="absolute",col=brewer.pal(8,'Pastel2'), main="Absolute Item Frequency Plot")

```

The Absolute Item Frequency Plot clearly indicates that the majority is the Coffee consummers, then bread, and so on.


```{r}

#Association rules which use Apriori Algorithm with support level 0.1%, and confidence level of 80%
association.rules <- apriori(TransData, parameter = list(supp=0.001, conf=0.80))

count(BreadBasket$Item)
itemsHere <- unique(BreadBasket$Item)
view(itemsHere)
count(itemsHere)

association.rules <- sort(association.rules, decreasing=TRUE,by="lift")

inspect(association.rules[1:5])

```

The first 5 association rules in order can be described as follow. 
87.50% of the customers who bought Extra Salami or Feta,Salad also bought Coffee,
86.67% of the customers who bought Pastry,Toast also bought Coffee,
85.71% of the customers who bought Hearty & Seasonal,Sandwich also bought Coffee,
83.33% of the customers who bought Cake,Vegan mincepie also bought Coffee,
83.33% of the customers who bought Salad,Sandwich also bought Coffee.
Overall, those selected transactions have lift above 1 , which means that there is a positive correlation between those items sets.

